Molecular transport in human pial perivasculature

### 2024-03-15 paper/main.tex
Updates from Overleaf
Former-commit-id: 8599a4326329a8560609bb3cbb3348554613dd74

Hodneland et al~\cite{hodneland2019new} developed a method to image the brains' microvasculature based on time-of-flight (ToF) and quantitative susceptibility mapping (QSM) to identify arterial and venous networks.

We derive a detailed tetrahedral mesh of both the parenchyma and the surrounding CSF-filled spaces alongside a network representation of the vasculature from the anatomical data provided therein.

>>>>

Hodneland et al~\cite{hodneland2019new} developed a method to image the brains' microvasculature based on time-of-flight (ToF) and quantitative susceptibility mapping (QSM) to identify arterial and venous networks.
We derive a detailed tetrahedral mesh of the parenchyma and the surrounding CSF-filled spaces alongside a network representation of the vasculature from the anatomical data provided therein.
